simulation for the sparse factor loadings

### 2018-01-28 analysis/GTEXzscoreTemplate.Rmd
Files commited by wflow_commit.

```{}
b_flash = readRDS("../data/GTExdata/res_flashr2/bflashvarcol.rds")
load("../data/GTExdata/gtexEQTL_zscore.rds")
ssY = sum(zscore^2)
K = dim(b_flash$EL)[2] -1
pve = (sapply(seq(1,K),function(x){ sum(b_flash$EL[,x]^2 %*% t(b_flash$EF[,x]^2)) }))/ssY
pve = pmax(round(pve,3),0.001)

@@

L = b_flash$EL[,1:14]
library(reshape2)
data_L = melt(L)
colnames(data_L) = c("tissue","loading","value")
library(ggplot2)
tissue_color = as.character(colordata[,2])
data_L$tissue = factor(data_L$tissue,levels = 1:44 ,labels = as.character(colordata[,1]) )
data_L$loading = factor(data_L$loading,levels = 1:14 ,labels = paste("loading",1:14,"; pve:", pve[1:14]))

ggplot(data_L,aes(x = tissue,y = value,fill = factor(tissue) )) +
  geom_bar(stat = "identity",width = 0.6) +
  scale_fill_manual(values=tissue_color) +
  scale_x_discrete(labels = NULL) +
  theme_grey()+
  theme(legend.position="right", legend.text=element_text(size=5), axis.text.y = element_text(size = 5)) + 
  labs(title = "GTEx data", y = "loading values" ,x = "tissues", fill="tissue") +
  facet_wrap(~loading, ncol = 2, scales = "free_y") +
  guides(fill = guide_legend(ncol = 1, keyheight = 0.5, keywidth = 0.5))
  ggsave("flashr2GTEx1.pdf", width = 8, height = 11)

# the 27th factor is zero
L = b_flash$EL[,15:26]
library(reshape2)
data_L = melt(L)
colnames(data_L) = c("tissue","loading","value")
library(ggplot2)
tissue_color = as.character(colordata[,2])
data_L$tissue = factor(data_L$tissue,levels = 1:44 ,labels = as.character(colordata[,1]) )
data_L$loading = factor(data_L$loading,levels = 1:12 ,labels = paste("loading",15:26,"; pve:", pve[15:26]))

ggplot(data_L,aes(x = tissue,y = value,fill = factor(tissue) )) +
  geom_bar(stat = "identity",width = 0.6) +
  scale_fill_manual(values=tissue_color) +
  scale_x_discrete(labels = NULL) +
  theme_grey()+
  theme(legend.position="right", legend.text=element_text(size=5), axis.text.y = element_text(size = 5)) + 
  labs(title = "GTEx data", y = "loading values" ,x = "tissues", fill="tissue") +
  facet_wrap(~loading, ncol = 2, scales = "free_y") +
  guides(fill = guide_legend(ncol = 1, keyheight = 0.5, keywidth = 0.5))
  ggsave("flashr2GTEx2.pdf", width = 8, height = 10)
```

>>>>

```{r}
b_flash = readRDS("../data/GTExdata/res_flashr2/bflashvarcol.rds")
load("../data/GTExdata/gtexEQTL_zscore.rds")
ssY = sum(zscore^2)
K = dim(b_flash$EL)[2] -1
pve = (sapply(seq(1,K),function(x){ sum(b_flash$EL[,x]^2 %*% t(b_flash$EF[,x]^2)) }))/ssY
pve = pmax(round(pve,3),0.001)

@@

L = b_flash$EL[,1:14]
library(reshape2)
data_L = melt(L)
colnames(data_L) = c("tissue","loading","value")
library(ggplot2)
tissue_color = as.character(colordata[,2])
data_L$tissue = factor(data_L$tissue,levels = 1:44 ,labels = as.character(colordata[,1]) )
data_L$loading = factor(data_L$loading,levels = 1:14 ,labels = paste("Factor",1:14,"; pve:", pve[1:14]))

ggplot(data_L,aes(x = tissue,y = value,fill = factor(tissue) )) +
  geom_bar(stat = "identity",width = 0.6) +
  scale_fill_manual(values=tissue_color) +
  scale_x_discrete(labels = NULL) +
  theme_grey()+
  theme(legend.position="right", legend.text=element_text(size=9), axis.text.y = element_text(size = 5)) + 
  labs(title = "GTEx data", y = "factor values" ,x = "tissues", fill="tissue") +
  facet_wrap(~loading, ncol = 2, scales = "free_y") +
  guides(fill = guide_legend(ncol = 1, keyheight = 0.8, keywidth = 0.3))
  #ggsave("flashr2GTEx1.pdf", width = 8, height = 11)

# the 27th factor is zero
L = b_flash$EL[,15:26]
library(reshape2)
data_L = melt(L)
colnames(data_L) = c("tissue","loading","value")
library(ggplot2)
tissue_color = as.character(colordata[,2])
data_L$tissue = factor(data_L$tissue,levels = 1:44 ,labels = as.character(colordata[,1]) )
data_L$loading = factor(data_L$loading,levels = 1:12 ,labels = paste("Factor",15:26,"; pve:", pve[15:26]))

ggplot(data_L,aes(x = tissue,y = value,fill = factor(tissue) )) +
  geom_bar(stat = "identity",width = 0.6) +
  scale_fill_manual(values=tissue_color) +
  scale_x_discrete(labels = NULL) +
  theme_grey()+
  theme(legend.position="right", legend.text=element_text(size=9), axis.text.y = element_text(size = 5)) + 
  labs(title = "GTEx data", y = "factor values" ,x = "tissues", fill="tissue") +
  facet_wrap(~loading, ncol = 2, scales = "free_y") +
  guides(fill = guide_legend(ncol = 1, keyheight = 0.8, keywidth = 0.3))
  #ggsave("flashr2GTEx2.pdf", width = 8, height = 10)
```

### 2018-01-28 analysis/simulation3.Rmd
Files commited by wflow_commit.

```{r}
gridExtra::grid.arrange(p0,p5,p6,p4,p1,p2,ncol = 2)
```

>>>>

```{r}
gridExtra::grid.arrange(p0,p2,p1,p6,p5,p4,ncol = 2)
```

## average of 100 simulations

```{r}
HMatrix = readRDS("../data/simulation/rankthree/HeatMap.rds")
T = 100
AVG_HM = matrix(0,nrow = 36000,ncol = 7)
for(i in 1:T){
  AVG_HM = AVG_HM + HMatrix[i,,]
}
AVG_HM = AVG_HM/100
```

```{r}
LF_1 = matrix(AVG_HM[,1],ncol = 240, nrow = 150)
LF_2 = matrix(AVG_HM[,2],ncol = 240, nrow = 150)
LF_3 = matrix(AVG_HM[,3],ncol = 240, nrow = 150)
LF_4 = matrix(AVG_HM[,4],ncol = 240, nrow = 150)
LF_5 = matrix(AVG_HM[,5],ncol = 240, nrow = 150)
LF_6 = matrix(AVG_HM[,6],ncol = 240, nrow = 150)
LF_true = matrix(AVG_HM[,7],ncol = 240, nrow = 150)
library(reshape2)
melted_cormat_1 <- melt(LF_1, na.rm = TRUE)
melted_cormat_2 <- melt(LF_2, na.rm = TRUE)
melted_cormat_3 <- melt(LF_3, na.rm = TRUE)
melted_cormat_4 <- melt(LF_4, na.rm = TRUE)
melted_cormat_5 <- melt(LF_5, na.rm = TRUE)
melted_cormat_6 <- melt(LF_6, na.rm = TRUE)
melted_cormat_true <- melt(LF_true, na.rm = TRUE)
# Heatmap
library(ggplot2)
plot_HP = function(title_name = "truth", melted_cormat){
  p1 = ggplot(data = melted_cormat, aes(Var2, Var1, fill = value))+
   geom_tile(color = "white")+
    scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
     midpoint = 0, limit = c(-0.25,0.25), space = "Lab") + labs(title = title_name, y = "samples", x = "variables") +
    theme_minimal() + theme(legend.position="none") 
  p1
}

p0 = plot_HP(title_name = "Truth", melted_cormat = melted_cormat_true)
p1 = plot_HP(title_name = "PMD.cv1", melted_cormat = melted_cormat_1)
p2 = plot_HP(title_name = "flash", melted_cormat = melted_cormat_2)
p3 = plot_HP(title_name = "flas_pn", melted_cormat = melted_cormat_3)
p4 = plot_HP(title_name = "SVD", melted_cormat = melted_cormat_4)
p5 = plot_HP(title_name = "SSVD", melted_cormat = melted_cormat_5)
p6 = plot_HP(title_name = "SI.cv", melted_cormat = melted_cormat_6)

```

```{r}
gridExtra::grid.arrange(p0,p2,p3,p1,p6,p5,p4,layout_matrix = rbind(c(NA,1,NA),c(2,3,4),c(5,6,7)))
```
